---
title: "Japan, Kuroshio Current, and Ryukyu Archipelago Study Area Report"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(targets)
library(sf)
```

## Introduction

This report documents the definition and creation of a study area encompassing Japan, the Ryukyu Archipelago, the Kuroshio Current region, Taiwan, the Ogasawara Islands, the Izu Islands, and coral reefs.

## Bounding Box

The study area is defined by the following bounding box:

```{r bounding_box}
tar_read(bounding_box)
```

## Data Layers

The following data layers were used to create the study area:

-   **Japan EEZ:** Exclusive Economic Zone of Japan.
-   **Ryukyu Archipelago:** The Ryukyu Archipelago region.
-   **Taiwan:**  The Taiwan region
-   **Ogasawara Islands:** The Ogasawara Islands, checked to be within the bounding box.
-   **Izu Islands:** The Izu Islands, checked to be within the bounding box.
-   **Coral Reefs:** Coral reef data from UNEP-WCMC (polygon data), clipped to the bounding box.

## Study Area Map

The final study area was created by combining these layers and clipping them to the bounding box.

```{r study_area_map, out.width='100%'}
tar_read(study_area_map)
```

## Data Output

The study area was saved as a GeoPackage file:

```{r data_output}
tar_read(save_study_area)
```